### 2019-02-21 sections/outlook.tex
add stub for abstract example
two minor changes in outlook

Firstly, we would like to express properties of tasks and prove them.
For example, one would like to prove that, no matter what, in Example~\ref{exm:abstract} a paper is always submitted.
Secondly, we would like to point out what it means for two tasks to be equal.
One could have noticed that some operators have a monadic or applicative feeling.
The combination of $\And$ and $\Edit$ could form a (lax) monoidal functor,
$\Or$ is similar to applicative choice,
and $\Then$ looks like a bind operation.
We need a correct understand of equivalency of tasks,
takin the interactive setting into account,
to prove this.
Thirdly, we do not know yet if the more complex combinators of \ITASKS are expressible in the basic combinators of \TOPHAT.
We implemented \TOPHAT on top of \ITASKS, so we know it is a subset,
but we also know \ITASKS can do more.

>>>>

Firstly, we would like to express properties of tasks and prove them.
For example, one would like to prove that, no matter what, in Example~\ref{exm:abstract} an abstract is always submitted.
Secondly, we would like explore what it means for two tasks to be equal.
One could have noticed that some operators have a monadic or applicative feeling.
The combination of $\And$ and $\Edit$ could form a (lax) monoidal functor,
$\Or$ is similar to applicative choice,
and $\Then$ looks like a bind operation.
We need a correct understand of equivalency of tasks,
taking the interactive setting into account,
to prove this.
Thirdly, we do not know yet if the more complex combinators of \ITASKS are expressible in the basic combinators of \TOPHAT.
We implemented \TOPHAT on top of \ITASKS, so we know it is a subset,
but we also know \ITASKS can do more.
